Spin canonical rings of log stacky curves

### 2015-07-07 curves-write-up/spin_cring.tex
move citation closer to author in intro

In particular, we bound the degrees of generators and relations of a
log spin canonical ring. Let
$\sx$ be a stacky curve with signature $\sigma = (g; e_1, \ldots,
e_r; \delta)$. The application of O'Dorney's work to log spin
canonical rings gives a weak bound in the case $g = 0$ in
terms of the least common multiples of the $e_i$'s \cite[Chapter 5]
{dorney:canonical}. In their treatment of log spin canonical
rings, Voight and Zureick-Brown \cite[Corollary 10.4.6]{vzb:stacky} bounded generator degrees by $6 \cdot \max(e_1, \ldots, e_r)$
and relation degrees by $12 \cdot \max(e_1, \ldots, e_r)$ when $\halfcan$ is effective. Note that the bounds we write here differ from those stated in Voight and Zureick-Brown \cite[Corollary 10.4.6]{vzb:stacky} by a factor of 2 because their grading convention differs from ours by a factor of 2.

>>>>

In particular, we bound the degrees of generators and relations of
a log spin canonical ring. Let $\sx$ be a stacky curve with
signature $\sigma = (g; e_1, \ldots, e_r; \delta)$. The application
of O'Dorney's work \cite[Chapter 5]{dorney:canonical} to log spin
canonical rings gives a weak bound in the case $g = 0$ in terms of
the least common multiples of the $e_i$'s. In their treatment of
log spin canonical rings, Voight and Zureick-Brown
\cite[Corollary 10.4.6]{vzb:stacky} bounded generator degrees by $6
\cdot \max(e_1, \ldots, e_r)$ and relation degrees by $12 \cdot \max
(e_1, \ldots, e_ r)$ when $\halfcan$ is effective. Note that the
bounds we write here differ from those stated in Voight and Zureick-
Brown \cite[Corollary 10.4.6]{vzb:stacky} by a factor of 2 because
their grading convention differs from ours by a factor of 2.
